### 2019-05-01 README.Rmd
Update README
Fix figure sizing in README

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-")
```
# robvis <img src="man/figures/robvis_hex_box.png" align="right" width="18%" height="18%" />

@@

    rob_summary_tools()
    [1] "ROB2"
    [1] "ROBINS-I"
    [1] "QUADAS-2"

@@

#### RoB2.0 tool for randomized controlled trials:
```{r out.width = "90%", fig.width= 12, fig.height=3}
plot_rob <- rob_summary(data = data_rob, tool = "ROB2")
plot_rob
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-", 
  out.width = "90%",
  fig.width= 12,
  fig.height=3)
```
# robvis <img src="man/figures/robvis_hex_box.png" align="right" width="18%" height="18%" />

@@

    rob_tools()
    [1] "ROB2"
    [1] "ROBINS-I"
    [1] "QUADAS-2"

@@

#### RoB2.0 tool for randomized controlled trials:
```{r}
plot_rob <- rob_summary(data = data_rob, tool = "ROB2")
plot_rob
```
